---
title: "Network"
author: "MD"
date: "'r format(Sys.time(), '%b %d, %Y')'"
output: 
 html_document:
   toc: true
   toc_float: true
   editor_options:
     chunk_output_type: console
   chunck_output_type: console
   chunk_output_type: console
---

install packages load libraries and load data
```{r}
library(chorddiag) # interactive chord diagrams
library(microeco) # statistical and plotting approaches in microbial community ecology
library(igraph) # for network analysis
library(rgexf) # to be exported to Gephi
library(RColorBrewer)
library(file2meco)
library(phyloseq)
```

```{r}
P.A <- emu_to_phyloseq(RA_file='/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/Minion_RhizoDD_1/EMU.rel_abund.finalRhizoDD1.csv',
                       meta_file='/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/Minion_RhizoDD_1/demultiplex_Rhizo_DD1.xlsx', 
                       sheet='Rhizo1', range='A1:S97',
                       sample_names='name',
                       run_name='Rhizo1')

P.B <- emu_to_phyloseq(RA_file='/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/Minion_RhizoDD_2/EMU.rel_abund.finalRhizoDD2.csv',
                       meta_file='/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/Minion_RhizoDD_2/demultiplex_Rhizo_DD2.xlsx', 
                       sheet='Rhizo2', range='A1:S92',
                       sample_names='name',
                       run_name='Rhizo2')

# merge all imported datasets
P.rel <- merge_phyloseq(P.A, P.B)
```

```{r import2}
# save combined relative abundance phyloseq object
saveRDS(P.rel, '/Users/derek_newberger/Desktop/Thesis_CSU/Cover_Crop_Peach/CC_R_Auto_Output/P.rel.RDS')

# convert EMU rel abundances to count data using final number of sequence reads
P.count <- P.rel
for (n in 1:nsamples(P.count)) {
  otu_table(P.count)[,n] <- round(otu_table(P.count)[,n] * sample_data(P.count)$final[n], 0)
}

# save combined count phyloseq object
saveRDS(P.count, '/Users/derek_newberger/Desktop/Thesis_CSU/Cover_Crop_Peach/CC_R_Auto_Output/P.count.RDS')
```

Create microtable environmenat from phyloseq data
```{r}
rank <- 'species'
P.glom <- tax_glom(P.count, taxrank=rank)
tax_table(P.glom) <- tax_table(P.glom)[,1:7]
taxa_names(P.glom) <- tax_table(P.glom)[,'species']

dataset <- phyloseq2meco(P.glom)
dataset

dataset$tidy_dataset()
dataset$sample_sums() %>% range
dataset$cal_abund()
dataset$save_abund(dirpath = "taxa_abund")


#subset to include data for each domestication group
group_W <- clone(dataset) #Whole Dataset

group_A<- clone(dataset)
group_A$sample_table <- subset(group_A$sample_table, Diversity == "A")
group_A$tidy_dataset()
group_A

group_B <- clone(dataset)
group_B$sample_table <- subset(group_B$sample_table, Diversity == "B")
group_B$tidy_dataset()
group_B

group_F <- clone(dataset)
group_F$sample_table <- subset(group_F$sample_table, Diversity == "F")
group_F$tidy_dataset()
group_F

group_AP <- clone(dataset)
group_AP$sample_table <- subset(group_AP$sample_table, Network == "AP")
group_AP$tidy_dataset()
group_AP

group_BP <- clone(dataset)
group_BP$sample_table <- subset(group_BP$sample_table, Network == "BP")
group_BP$tidy_dataset()
group_BP

group_FP <- clone(dataset)
group_FP$sample_table <- subset(group_FP$sample_table, Network == "FP")
group_FP$tidy_dataset()
group_FP

```

Generate networks for monocropping and grouped polycrop
```{r}
networkW <- trans_network$new(dataset = dataset, cor_method = "spearman", filter_thres = 0.001)
networkW$cal_network(COR_p_thres = 0.01, COR_optimization = TRUE)
networkW$cal_module(method = "cluster_fast_greedy")
networkW$save_network(filepath = "/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/RhizoDD_Output/example.gexf")

networkA <- trans_network$new(dataset = group_A, cor_method = "spearman", filter_thres = 0.001)
networkA$cal_network(COR_p_thres = 0.01, COR_optimization = TRUE)
networkA$cal_module(method = "cluster_fast_greedy")
networkA$save_network(filepath = "/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/RhizoDD_Output/Alfalfa.gexf")

networkB <- trans_network$new(dataset = group_B, cor_method = "spearman", filter_thres = 0.001)
networkB$cal_network(COR_p_thres = 0.01, COR_optimization = TRUE)
networkB$cal_module(method = "cluster_fast_greedy")
networkB$save_network(filepath = "/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/RhizoDD_Output/Brassica.gexf")

networkF <- trans_network$new(dataset = group_F, cor_method = "spearman", filter_thres = 0.001)
networkF$cal_network(COR_p_thres = 0.01, COR_optimization = TRUE)
networkF$cal_module(method = "cluster_fast_greedy")
networkF$save_network(filepath = "/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/RhizoDD_Output/Fescue.gexf")

networkAP <- trans_network$new(dataset = group_AP, cor_method = "spearman", filter_thres = 0.001)
networkAP$cal_network(COR_p_thres = 0.01, COR_optimization = TRUE)
networkAP$cal_module(method = "cluster_fast_greedy")
networkAP$save_network(filepath = "/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/RhizoDD_Output/AlfalfaP.gexf")

networkBP <- trans_network$new(dataset = group_BP, cor_method = "spearman", filter_thres = 0.001)
networkBP$cal_network(COR_p_thres = 0.01, COR_optimization = TRUE)
networkBP$cal_module(method = "cluster_fast_greedy")
networkBP$save_network(filepath = "/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/RhizoDD_Output/BrassicaP.gexf")

networkFP <- trans_network$new(dataset = group_FP, cor_method = "spearman", filter_thres = 0.001)
networkFP$cal_network(COR_p_thres = 0.01, COR_optimization = TRUE)
networkFP$cal_module(method = "cluster_fast_greedy")
networkFP$save_network(filepath = "/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/RhizoDD_Output/FescueP.gexf")
```

Create microtable environment from phyloseq data for polyculture separate
```{r}
group_Ab<- clone(dataset)
group_Ab$sample_table <- subset(group_Ab$sample_table, Diversity == "Ab")
group_Ab$tidy_dataset()
group_Ab

group_Af<- clone(dataset)
group_Af$sample_table <- subset(group_Af$sample_table, Diversity == "Af")
group_Af$tidy_dataset()
group_Af

group_Abf<- clone(dataset)
group_Abf$sample_table <- subset(group_Abf$sample_table, Diversity == "Abf")
group_Abf$tidy_dataset()
group_Abf

group_Ba<- clone(dataset)
group_Ba$sample_table <- subset(group_Ba$sample_table, Diversity == "Ba")
group_Ba$tidy_dataset()
group_Ba

group_Bf<- clone(dataset)
group_Bf$sample_table <- subset(group_Bf$sample_table, Diversity == "Bf")
group_Bf$tidy_dataset()
group_Bf

group_Baf<- clone(dataset)
group_Baf$sample_table <- subset(group_Baf$sample_table, Diversity == "Baf")
group_Baf$tidy_dataset()
group_Baf

group_Fa<- clone(dataset)
group_Fa$sample_table <- subset(group_Fa$sample_table, Diversity == "Fa")
group_Fa$tidy_dataset()
group_Fa

group_Fb<- clone(dataset)
group_Fb$sample_table <- subset(group_Fb$sample_table, Diversity == "Fb")
group_Fb$tidy_dataset()
group_Fb

group_Fab<- clone(dataset)
group_Fab$sample_table <- subset(group_Fab$sample_table, Diversity == "Fab")
group_Fab$tidy_dataset()
group_Fab
```

Generate networks for each polycrop treatment grouped by density
```{r}
networkAb <- trans_network$new(dataset = group_Ab, cor_method = "spearman", filter_thres = 0.001)
networkAb$cal_network(COR_p_thres = 0.01, COR_optimization = TRUE)
networkAb$cal_module(method = "cluster_fast_greedy")
networkAb$save_network(filepath = "/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/RhizoDD_Output/Ab.gexf")

networkAf <- trans_network$new(dataset = group_Af, cor_method = "spearman", filter_thres = 0.001)
networkAf$cal_network(COR_p_thres = 0.01, COR_optimization = TRUE)
networkAf$cal_module(method = "cluster_fast_greedy")
networkAf$save_network(filepath = "/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/RhizoDD_Output/Af.gexf")

networkAbf <- trans_network$new(dataset = group_Abf, cor_method = "spearman", filter_thres = 0.001)
networkAbf$cal_network(COR_p_thres = 0.01, COR_optimization = TRUE)
networkAbf$cal_module(method = "cluster_fast_greedy")
networkAbf$save_network(filepath = "/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/RhizoDD_Output/Abf.gexf")

networkBa <- trans_network$new(dataset = group_Ba, cor_method = "spearman", filter_thres = 0.001)
networkBa$cal_network(COR_p_thres = 0.01, COR_optimization = TRUE)
networkBa$cal_module(method = "cluster_fast_greedy")
networkBa$save_network(filepath = "/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/RhizoDD_Output/Ba.gexf")

networkBf <- trans_network$new(dataset = group_Bf, cor_method = "spearman", filter_thres = 0.001)
networkBf$cal_network(COR_p_thres = 0.01, COR_optimization = TRUE)
networkBf$cal_module(method = "cluster_fast_greedy")
networkBf$save_network(filepath = "/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/RhizoDD_Output/Bf.gexf")

networkBaf <- trans_network$new(dataset = group_Baf, cor_method = "spearman", filter_thres = 0.001)
networkBaf$cal_network(COR_p_thres = 0.01, COR_optimization = TRUE)
networkBaf$cal_module(method = "cluster_fast_greedy")
networkBaf$save_network(filepath = "/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/RhizoDD_Output/Baf.gexf")

networkFa <- trans_network$new(dataset = group_Fa, cor_method = "spearman", filter_thres = 0.001)
networkFa$cal_network(COR_p_thres = 0.01, COR_optimization = TRUE)
networkFa$cal_module(method = "cluster_fast_greedy")
networkFa$save_network(filepath = "/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/RhizoDD_Output/Fa.gexf")

networkFb <- trans_network$new(dataset = group_Fb, cor_method = "spearman", filter_thres = 0.001)
networkFb$cal_network(COR_p_thres = 0.01, COR_optimization = TRUE)
networkFb$cal_module(method = "cluster_fast_greedy")
networkFb$save_network(filepath = "/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/RhizoDD_Output/Fb.gexf")

networkFab <- trans_network$new(dataset = group_Fab, cor_method = "spearman", filter_thres = 0.001)
networkFab$cal_network(COR_p_thres = 0.01, COR_optimization = TRUE)
networkFab$cal_module(method = "cluster_fast_greedy")
networkFab$save_network(filepath = "/Users/derek_newberger/Desktop/Thesis_CSU/Rhizo_Density_Diversity/RhizoDD_Output/Fab.gexf")
```


```{r}
print(networkFab)
```

Generate chord diagrams for each domesitication group
```{r}
networkW$cal_sum_links(taxa_level = "phylum")
networkW$plot_sum_links(plot_pos = TRUE, plot_num = 10, color_values = brewer.pal(10, "Paired"))
```

```{r}
networkA$cal_sum_links(taxa_level = "species")
networkA$plot_sum_links(plot_pos = TRUE, plot_num = 10, color_values = brewer.pal(10, "Paired"))
```

```{r}
networkB$cal_sum_links(taxa_level = "species")
networkB$plot_sum_links(plot_pos = TRUE, plot_num = 10, color_values = brewer.pal(10, "Paired"))
```

```{r}
networkF$cal_sum_links(taxa_level = "species")
networkF$plot_sum_links(plot_pos = TRUE, plot_num = 10, color_values = brewer.pal(10, "Paired"))
```
